% =============================================================================
\section{Examples}
% =============================================================================
%
Xilinx ISE 14.7 supports Verilog and VHDL, and does not support SystemVerilog.
The example designs are all written in VHDL. Virtex-5 designs can be developed
using SystemVerilog, however the code must be synthesized to EDIF using a 
synthesis tool like Synopsys Synplify, and then the EDIF passed to Xilinx ISE 
for place-and-route and bitstream generation.

% -----------------------------------------------------------------------------
\subsection{Blinky LEDs}
% -----------------------------------------------------------------------------
%
The first design that is useful to create on a development kit is a blinky
LEDs design. This design helps confirm the presence of a clock, and correct
pin assignments.
%
Table~\ref{tab:blinky_pins} shows the schematic net names for the clocks and
the LEDs. The blinky LED design will use the 100MHz clock on GLK0.
%
This section walks through the manual implementation of the blinky design, 
and then the design is scripted for easier regeneration.

The Virtex-5 Blinky design is generated as follows;
%
\begin{enumerate}
\item Start the Xilinx ISE 14.7 VM and map the shared drive.
\item Start Xilinx ISE 14.7.
% -------------------------
\item Create a new project.
% -------------------------

Select \emph{File$\rightarrow$New Project}

In the \emph{Create New Project} dialog, enter:
%
\begin{itemize}
\item Name: genesys
\item Location: /mnt/c/github/digilent\_genesys/designs/blinky/build
\item Working Directory: /mnt/c/github/digilent\_genesys/designs/blinky/build
\end{itemize}
%
and then click \emph{Next}.

In the \emph{Project Settings} dialog, make the following changes:
%
\begin{itemize}
\item Family: Virtex5
\item Device: XC5VLX50T
\item Package: FF1136
\item Speed: -1
\item Preferred Language: VHDL
\item VHDL Source Analysis Standard: VHDL-200X
\end{itemize}
%
and then click \emph{Next}, and then \emph{Finish}.

% -------------------------------
\item Add the blinky source code.
% -------------------------------
\begin{itemize}
\item Select \emph{Project$\rightarrow$Add Source}
\item Add the top-level source file \verb+designs/blinky/src/genesys.vhd+. 
\end{itemize}

% -------------------------------
\item Synthesize and Implement the design.
% -------------------------------

Click the green run button to run \verb+Synthesis - XST+ and \verb+Implement Design+.

If implementation fails with the error message:
%
\begin{quote}
\texttt{\textcolor{magenta}{ERROR}:Map:258 - A problem was encountered 
attempting to get the license\newline for this architecture.}
\end{quote}
%
Then check the Xilinx ISE license manager settings.

\end{enumerate}



% -----------------------------------------------------------------------------
% Blinky LEDs pin constraints
% -----------------------------------------------------------------------------
%
\begin{table}[t]
\caption{Digilent Genesys Blinky LEDs pin constraints.}
\label{tab:blinky_pins}
\begin{center}
\begin{tabular}{|l||c|c|c|c|c|c|}
\hline
Net Name       & Pin & Bank & Voltage & I/O Standard & Drive & Slew\\
\hline\hline
&&&&&&\\
\verb+GCLK0+   & AG18 &   4 & 3.3V & LVCMOS3V3 &&\\
&&&&&&\\
\verb+GCLK2+   & AE13 &   2 & 3.3V & LVCMOS3V3 &&\\
&&&&&&\\
\verb+GCLK4_P+ & J14  &   3 & 2.5V & LVDS &&\\
\verb+GCLK4_N+ & H13  &   3 & 2.5V & LVDS &&\\
&&&&&&\\
\verb+GCLK5_P+ & H19  &   3 & 3.3V & LVDS &&\\
\verb+GCLK5_n+ & H20  &   3 & 3.3V & LVDS &&\\
&&&&&&\\
\verb+GCLKS+   & AH15 &   4 & 3.3V & LVCMOS3V3 &&\\
&&&&&&\\
\verb+LD[0]+   & AG8  &  22 & 3.3V & LVCMOS3V3 & 4mA & SLOW\\
\verb+LD[1]+   & AH8  &  22 & 3.3V & LVCMOS3V3 & 4mA & SLOW\\
\verb+LD[2]+   & AH9  &  22 & 3.3V & LVCMOS3V3 & 4mA & SLOW\\
\verb+LD[3]+   & AG10 &  22 & 3.3V & LVCMOS3V3 & 4mA & SLOW\\
\verb+LD[4]+   & AH10 &  22 & 3.3V & LVCMOS3V3 & 4mA & SLOW\\
\verb+LD[5]+   & AG11 &  22 & 3.3V & LVCMOS3V3 & 4mA & SLOW\\
\verb+LD[6]+   & AF11 &  22 & 3.3V & LVCMOS3V3 & 4mA & SLOW\\
\verb+LD[7]+   & AE11 &  22 & 3.3V & LVCMOS3V3 & 4mA & SLOW\\
&&&&&&\\
\hline
\end{tabular}
\end{center}
\end{table}
% -----------------------------------------------------------------------------
